### 2019-11-25 paper/results.tex
last version before submission

\section{Results and discussion} \label{Results-and-discussion}
The molar fraction of the heavy metal (HM) 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases (see Table~\ref{tab:table4}). 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL).
\subsection{Thorium feed mechanism}
The thorium feed mechanism continuously feeds thorium from the external stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}.
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products (FPs). The amount of $^{233}$U generated in 
the SD-TMSR is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. For U-233 case, 
the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
\gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1} (U-233 case)).
Notably, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
For the HALEU fuel salt, the amount of $^{233}$U generated in the SD-TMSR after a few years is insufficient to counteract the absorption of the (non-fissile) $^{238}$U added at start-up after much of the original $^{235}$U is depleted. Consequently, the core becomes subcritical after $\approx$ $6$ years of operation.
For the reactor-grade Pu fuel salt, the core becomes subcritical after $\approx$ $12$ years because the amount of $^{233}$U generated is not sufficient to counteract the neutron absorption in the non-fissile plutonium isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.

@@

\subsection{Non-thorium feed mechanism}
The non-thorium feed mechanism continuously feeds 
$^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}).
Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
without $^{232}$Th will lead to a supercritical reactor, thus the $^{233}$U case 
is excluded from the non-thorium feed mechanism study.
Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both the reactor-grade Pu and TRU cases 
show promising results relative to the other two cases (HALEU and Pu+HALEU) (see Figure~\ref{fig:keff2}). 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff2.png}
			\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 
	\gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence 
	interval $\pm\sigma$ is shaded).} 
	\label{fig:keff2}
\end{figure}
For the reactor-grade Pu case, the amount of $^{233}$U generated in the \gls{SD-TMSR}, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs. 
For the \gls{TRU} fuel salt, the amount of 
$^{233}$U and the external feed flow of TRU is barely enough to operate the 
reactor for a long period of time ($\approx$ $40$ years) without any 
external feed of $^{233}$U ($^{233}$U used only from the \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
because of the \glspl{MA}\footnote{In the present work, the minor actinides 
(MA) include Np, Am, and Cm.} accumulating in the core as a result of 
continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the HALEU and Pu+HALEU 
fuel are less attractive for the non-thorium feed mechanism. The continuous HALEU 
feed increases the amount of fertile $^{238}$U and consequently, reduces the 
feasibility of such fissile materials. According to the $k_{eff}$ 
results, reactor-grade Pu and TRU are the only alternative fissile materials that  
can be used to startup and maintain operation of the \gls{SD-TMSR}.

@@

Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
reactor operation for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
zero. 
Although all produced $^{233}$U is used to refuel the core, the reactor is subcritical after $40$ years of operation (see Figure~\ref{fig:keff2}).
In the $^{233}$U and reactor-grade Pu cases, the net production of 
$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$ at EOL, respectively. Figure~\ref{fig:NetCC} shows that for the $^{233}$U 
case the net production of $^{233}$U during the first 455 days is negative; 
about $175.28$ $kg$ of $^{233}$U must be added during this period. 
As shown in Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR}. Similarly, 
one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
after $\approx$ $4.5$ years if we apply the non-thorium feed mechanism on 
the SD-TMSR that was initially loaded by reactor-grade Pu alternative to 
$^{233}$U. For nonproliferation reasons, $^{233}$U could be diluted with $^{238}$U which makes it impossible to use for nuclear weapons.

>>>>

\section{Results and discussion} \label{Results-and-discussion}
The molar fraction of the heavy metal (HM) 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases (see Table~\ref{tab:table4}). 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL).
\subsection{Thorium feed mechanism}
The thorium feed mechanism continuously feeds thorium from the external stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}.
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products (FPs). The amount of $^{233}$U generated in 
the SD-TMSR is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. For U-233 case, 
the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
\gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1}, U-233 case).

Notably, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
For the HALEU fuel salt, the amount of $^{233}$U generated in the SD-TMSR after a few years is insufficient to counteract the absorption of the (non-fissile) $^{238}$U added at start-up after much of the original $^{235}$U is depleted. Consequently, the core becomes subcritical after $\approx$ $6$ years of operation.
For the reactor-grade Pu fuel salt, the core becomes subcritical after $\approx$ $12$ years because the amount of $^{233}$U generated is not sufficient to counteract the neutron absorption in the non-fissile plutonium isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.

@@

\subsection{Non-thorium feed mechanism}
The non-thorium feed mechanism continuously feeds 
$^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}).
Under the non-thorium feed mechanism, only four different initial fissile materials are studied: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
without $^{232}$Th will lead to a supercritical reactor, thus the $^{233}$U case 
is excluded from the non-thorium feed mechanism study.
Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both the reactor-grade Pu and TRU cases 
show promising results relative to the other two cases (HALEU and Pu+HALEU) (see Figure~\ref{fig:keff2}). 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff2.png}
			\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 
	\gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence 
	interval $\pm\sigma$ is shaded).} 
	\label{fig:keff2}
\end{figure}
For the reactor-grade Pu case, the amount of $^{233}$U generated in the \gls{SD-TMSR}, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs. 
For the \gls{TRU} fuel salt, the amount of 
$^{233}$U and the external feed flow of TRU is barely enough to operate the 
reactor for a long period of time ($\approx$ $40$ years) without any 
external feed of $^{233}$U ($^{233}$U used only from the \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
because of the \glspl{MA}\footnote{In the present work, the minor actinides 
(MA) include Np, Am, and Cm.} accumulating in the core as a result of 
continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the HALEU and Pu+HALEU 
fuel are less attractive for the non-thorium feed mechanism. The continuous HALEU 
feed increases the amount of fertile $^{238}$U and consequently, reduces the 
feasibility of such fissile materials. According to the $k_{eff}$ 
results, reactor-grade Pu and TRU are the only alternative fissile materials that  
can be used to startup and maintain operation of the \gls{SD-TMSR}.

@@

Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
reactor operation for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
zero. 
Although all produced $^{233}$U is used to refuel the core, the reactor is subcritical after $40$ years of operation (see Figure~\ref{fig:keff2}).
In the $^{233}$U and reactor-grade Pu cases, the net production of 
$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$ at EOL, respectively. Figure~\ref{fig:NetCC} shows that for the $^{233}$U 
case the net production of $^{233}$U during the first 455 days is negative; 
about $175.28$ $kg$ of $^{233}$U must be added during this period. 
As shown in Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR} (see Table~\ref{tab:table5}). Similarly, 
one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
after $\approx$ $4.5$ years if we apply the non-thorium feed mechanism on 
the SD-TMSR that was initially loaded by reactor-grade Pu alternative to 
$^{233}$U. For nonproliferation reasons, $^{233}$U could be diluted with $^{238}$U which makes it impossible to use for nuclear weapons.
